Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010

### 2017-03-04 ms.tex
I replaced the time series plots with a Python version that also shows the maximum likelihood models.
I adjusted the descriptions of the Mie scattering fits.

\begin{figure*}[!t]
\centering
\subfloat[2MASS J0835]{
	\includegraphics[width=0.5\textwidth]{2mass_0835_t_series.png}
	\label{fig:tserPhase0835}
	}
\subfloat[2MASS J1821]{
	\includegraphics[width=0.5\textwidth]{2mass_1821_t_series.png}
	\label{fig:tserPhase1821}
	}
	\caption{Time series for each system with an offset added for clarity. Each wavelength bin is labeled on the right side. Alternating colors are used to distinguished the light curves with offsets. \sha\ shows relatively flat light curves whereas \shb\ has large amplitude double-peaked oscillations at short wavelengths and flat light curves at long wavelengths.}
	\label{fig:tserPfold}
\end{figure*}

\begin{figure*}
\centering
\subfloat[2MASS J0835]{
	\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j0835.pdf}
	\label{fig:ampspec0835}
	}
\subfloat[2MASS J1821]{
	\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821.pdf}
	\label{fig:ampspec1821}
	}
	\caption{Sine fit amplitude versus wavelength for each brown dwarf. \sha\ shows no clear trend in wavelength, while \shb\ has a strong slope indicative of Mie-scattering particles.
	 Also shown in the figure for \shb\ is the WFC3 amplitude from \citet{2015ApJ...798L..13Y}. The WFC3 observations were from a different epoch, with different cloud coverage, but show a similar slope.
	 The amplitude spectrum for \shb\ is fit with a simple Mie scattering models for a log-normal particle size distribution of spherical forsterite grains with a best-fit radius of 0.17 grains.}
	\label{fig:ampSpec}
\end{figure*}

@@

We model the wavelength dependence of 2MASS 1821 as an optically thin cloud layer consisting of a log-normal distribution of particle sizes.
If we assume the cloud covers one hemisphere of the brown dwarf, the amplitude of the variability ($A$) is directly proportional to the opacity of the particles.
We model the single particle extinction coefficient, $Q_{ext}$ from the \texttt{Python} Mie theory code \texttt{miescatter} \citep{bohren1983mie} to calculate the opacity as a function of wavelength.
We assume that the particles are spherical forsterite grains (Mg$_2$SiO$_4$).
We use a constant n=1.67 - 0.006 $j$ index of refraction because the real and imaginary parts of the index of refraction are relatively constant across the optical and near infrared \citep{scott1996forsterite}.

For the particle size distribution we assume a log-normal distribution around a characteristic size, $s$ and a standard deviation of the logarithm (scale parameter), $\sigma$ =0.5.
The spectral dependence is therefore modeled as 
\begin{equation}
A = B \bar{Q_{avg}}(r)
\end{equation}
where $A_1$ is the amplitude, $B$ is a constant encapsulating the area and column density and $\bar{Q_{avg}}(r)$ is the average extinction coefficient averaged over all particles in the log-normal distribution with a median radius of $r$.

Figure \ref{fig:ampspec1821} shows the best-fit model which has a median particle radius of 0.16~$\mu$m grains.
This model has a reduced $\chi^2$ of 0.99 and is consistent with the measured amplitude spectrum.
Figure \ref{fig:corner1821mie} shows the posterior distribution for the $B$ and $r$ parameters.
The derived median particle radius of $r$=0.164 $^{+0.012}_{-0.007}$~$\mu$m is a vary tight constraint for particle size median.
Considering the large number of possible grain geometries and compositions, this is an underestimate for the true uncertainty in median particle size.

>>>>

\begin{figure*}[!t]
\centering
\subfloat[2MASS J0835]{
	\includegraphics[width=0.5\textwidth]{2mass_0835_t_series.pdf}
	\label{fig:tserPhase0835}
	}
\subfloat[2MASS J1821]{
	\includegraphics[width=0.5\textwidth]{2mass_1821_t_series.pdf}
	\label{fig:tserPhase1821}
	}
	\caption{Time series for each system with an offset added for clarity. Each wavelength bin is labeled on the right side. Changing colors are used to distinguished the light curves with offsets. \sha\ shows relatively flat light curves whereas \shb\ has large amplitude double-peaked oscillations at short wavelengths and flat light curves at long wavelengths.}
	\label{fig:tserPfold}
\end{figure*}

\begin{figure*}
\centering
\subfloat[2MASS J0835]{
	\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j0835.pdf}
	\label{fig:ampspec0835}
	}
\subfloat[2MASS J1821]{
	\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821.pdf}
	\label{fig:ampspec1821}
	}
	\caption{Sine fit amplitude versus wavelength for each brown dwarf. \sha\ shows no clear trend in wavelength, while \shb\ has a strong slope indicative of Mie-scattering particles.
	 Also shown in the figure for \shb\ is the WFC3 amplitude from \citet{2015ApJ...798L..13Y}. The WFC3 observations were from a different epoch, with different cloud coverage, but show a similar slope.
	 The amplitude spectrum for each system is fit a simple Mie scattering model for a log-normal particle size distribution of spherical forsterite grains.
	 \sha\ is consistent with a zero amplitude flat amplitude model which essentially puts no constraints on the particle size distribution.
	 \shb\ is shown with the best fit median particle size of 0.17 $\mu$m grains.}
	\label{fig:ampSpec}
\end{figure*}

@@

We model the wavelength dependence of \sha\ and \shb\ with a simple cloud model: an optically thin cloud layer consisting of a log-normal distribution of particle sizes.
If we assume the cloud covers one longitudinal hemisphere of the brown dwarf, the amplitude of the variability ($A$) is directly proportional to the opacity of the particles.
We model the single particle extinction coefficient, $Q_{ext}$ from the \texttt{Python} Mie theory code \texttt{miescatter} \citep{bohren1983mie} to calculate the opacity as a function of wavelength.
We assume that the particles are spherical forsterite grains (Mg$_2$SiO$_4$).
We use a constant n=1.67 - 0.006 $j$ index of refraction because the real and imaginary parts of the index of refraction are relatively constant across the optical and near infrared \citep{scott1996forsterite}.

For the particle size distribution we assume a log-normal distribution around a characteristic size, $s$ and a standard deviation of the logarithm (scale parameter), $\sigma$ =0.5.
The spectral dependence is therefore modeled as 
\begin{equation}
A = B \bar{Q_{avg}}(r)
\end{equation}
where $A_1$ is the amplitude, $B$ is a constant encapsulating the area and column density and $\bar{Q_{avg}}(r)$ is the average extinction coefficient averaged over all particles in the log-normal distribution with a median radius of $r$.
When fitting the amplitude spectra to our Mie model, we impose a prior on the maximum median particle size radius ($0 \mu m < r < 5 \mu m$).

For \sha\ we find that since no significant variability is detected that the particle size is unconstrained over the prior of $0 \mu < r < 5 \mu m$).
We show the maximum likelihood particle radius of 2.3 $\mu$m
Figure \ref{fig:ampspec1821} shows the best-fit model which has a median particle radius of 0.16~$\mu$m grains.
This model has a reduced $\chi^2$ of 0.99 and is consistent with the measured amplitude spectrum.
Figure \ref{fig:corner1821mie} shows the posterior distribution for the $B$ and $r$ parameters.
The derived median particle radius of $r$=0.164 $^{+0.012}_{-0.007}$~$\mu$m is a vary tight constraint for particle size median.
Considering the large number of possible grain geometries and compositions, this is an underestimate for the true uncertainty in median particle size.
